In this chapter, we will present the results obtained from 
four cases with the numerical simulation of the Navier Stokes 
equation using the vorticity-streamfunction formulation with 
the species transport equation, where we have incompressible 
and monophase two-dimensional flow for all cases
in an Arbitrary Lagrangian-Eulerian context
using the semi-Lagrangian Method. 
In all simulations, were considered the $\beta_{1}=0$ 
and $\beta_{2}=1$. 
Therefore, the computational mesh velocity is
calculated using only the Laplacian smoothing velocity.

\medskip
The first section is about \textit{Couette flow} and 
the numerical solution is compared with the analytical solution. 
The second section is about the \textit{Poiseuille flow},
where the no-slip condition is applied 
and the numerical solution is also compared with 
the analytical solution. The third section refers to the flow 
of \textit {Poiseuille} in the half domain, where the 
free slip condition is applied on the axis of symmetry. 
The fourth section refers to the (\textit{lid-driven cavity flow}) 
and the solution is compared with the results presented 
by Ghia et al. (1982) \cite{ghia1982} and 
Marchi et al. (2009) \cite{marchi2009} for several Reynold numbers. 
Lastly, the comparison of the semi-Lagrangian Method in a unstructured
linear and quadratic triangular mesh is done
for the transport of a scalar 
submitted to a pure advection flow is presented.

\medskip
All numerical simulations were performed on the computers 
of \textit {Numerical Simulations Laboratory (LEN)} 
of \textit {Environmental Simulations in Reservoirs and 
Study Group (GESAR)} with the following configuration:

\begin{itemize}
 \item AMD FX-8350 4GHz with 8 core, 32Gb RAM Memory, 1000Gb of HD.
       LINUX Ubuntu 16.04 LTS. The numerical code implementarion was
       performed using Python 2.7 language
\end{itemize}

\newpage
